Bone-Conduction and Spatialised Audio to Guide People with Visual Impairments

### 2019-07-15 paper.tex
Added reference, removed wrong statement. Fixed todo

\title{Bone-Conduction Audio Interface to\\Guide People with Visual Impairments}
\titlerunning{Guiding People with Bone-Conduction and Spatialised Audio}

@@

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with vision impairments report that they prefer haptic and vocal feedback out of the three options. \todo{ref blind preferences}
However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions.\tofix{reference?}
Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.

@@

Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
The binaural cues include ITD and ILD that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
%The user's anatomy acts as a filter and the direction the sound wave hits the body activates different filter resonances, attenuating or accentuating different frequency bands.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one does.

@@

The guidance target is presented to the user in terms of pan and elevation angles, indicating the angle adjustments that are required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\cite{klatzky2006cognitive}.
However, the audio guidance signals are delivered to the user with a set of bone-conduction headphones that bypass the user's outer-ear structure and since this structure plays an important role in localising a sound source's elevation\cite{blauert1969sound}, an alternative mode of conveying the elevation angle is required.\todo{check repeating from hardware selection section}
Therefore, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conduction headphones\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.

@@

The human audition system uses binaural comparison cues, such as the inter-aural time and level differences (ITD and ILD respectively), to localise a sound source on the horizontal plane~\cite{blauert1969sound}.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right, will hit the right ear first with a slightly higher volume.

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous research results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.37}{\radian} and \SI{0.51}{\radian} for groups \textit{G1} and \textit{G2} respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 46\% and 26\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a lesser improvement (11\%) with \textit{G1} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization} and a 18\% reduction in performance for group \textit{G2}.
However, the participants from~\cite{stanley2006lateralization} all had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for group \textit{G2} are centred around the negative angle, indicating a possible underlying bias in the participants or the interface.
A similar trend was observed in~\cite{stanley2006lateralization} and warrants an investigation with a larger participant pool to determine the underlying bias, if any.

The error data was used to generate scatter plots that show the correlation between the position that the guidance system presented the participants and the position the participants thought the targets were.
These plots are given in \cref{fig:correlation-results} and show a reasonably positive correlation between the guidance targets and the selected targets, which indicates that the participants correctly interpreted the interface's output for the most part. 
The Pearson correlation scores for each dataset, listed in \cref{tab:results}, confirm this.

@@

Future work will involve a more in-depth investigation with a larger participant pool to determine the factors that affect performance and enable a more detailed statistical analysis.
For example, will adjusting the elevation function's gradient make it easier to guess the target's elevation and what is the performance difference between participants with limited and healthy eyesight?  
Furthermore, experiments with a large group of people with vision impairments will provide an opportunity to gauge their opinion on the interface and identify possible avenues of improvements to user friendliness.

>>>>

%\title{Bone-Conduction Audio Interface to\\Guide People with Visual Impairments}
\title{Bone-Conduction and Spatialised Audio to Guide People with Visual Impairments}

@@

Multiple mobile navigation and travel aids have been devised throughout the years, some as part of a commercial undertaking and many as part of academic research.
The majority of these systems rely on one or a combination of vocal~\cite{mocanu2016when,chessa2016integrated,kanwal2015navigation}, audio~\cite{schwarze2015intuitive,rodriguez2012obstacle,katz2010navig} and haptic~\cite{rivera-rubio2015assistive,lee2015rgb,xiao2015assistive} feedback media to communicate guidance instructions to the user, each with their own sets of features and limitations.
In general, participants with vision impairments report that they prefer haptic and vocal feedback out of the three options~\cite{arditi2013user}.
However, haptic feedback systems typically have extra hardware requirements to transmit the guidance instructions.
Furthermore, haptic and vocal feedback can become a cognitive burden, particularly where high resolution guidance, which can exceed the bandwidth of these particular senses, is required.
Indeed, participants report that they would prefer control over the vocal feedback channel and trigger guidance instructions, instead of being given constant guidance instructions.\tofix{reference?}
Simple audio tones are less affected by these bandwidth and hardware limitations, but they can potentially fatigue the user's senses if too unpleasant.

@@

Humans localise a sound source in 3 dimensions by considering cues recorded in one ear (monaural cues) and comparing cues received at both ears (binaural cues)~\cite{blauert1997spatial,blauert1969sound}.
The binaural cues include inter-aural time and level differences (ITD and ILD respectively) that help to determine a source's location on the horizontal plane.
Monaural cues are taken from the interaction of the sound with the human anatomy, e.g.\ head, shoulders, outer ear, before it enters the ear canal.
%The user's anatomy acts as a filter and the direction the sound wave hits the body activates different filter resonances, attenuating or accentuating different frequency bands.
When the modified audio signal enters the inner ear canal, the human brain is able to analyse the frequency response and accurately determine the position of the sound source on the median plane. 
The distance to the source is simply derived as the intensity, or volume, of the source, i.e.\ a louder sound would appear closer to the user than a softer one does.

@@

The guidance target is presented to the user in terms of pan and elevation angles, indicating the angle adjustments that are required to point the device camera at the target location, as shown in \cref{fig:cam-coords}.
Spatialised audio signals are well-suited to the task, displaying similar levels of performance to vocal feedback, but with less cognitive load and higher resolution~\cite{klatzky2006cognitive}.
However, given the previously discussed limitations of bone-conduction and spatialised audio, we propose a simple linear adjustment to the signal's pitch as a function of the elevation angle. 
The pan angle can be conveyed by transforming the audio signal with an HRTF, and indeed it has been found that this dimension is unaffected by using bone-conducting headphones\cite{schonstein2008comparison,macdonald2006spatial,stanley2006lateralization}.

@@

The human audition system uses binaural comparison cues, such as ITD and ILD, to localise a sound source on the horizontal plane~\cite{blauert1969sound}.
The ITD is the perceived time delay between the signal reaching both ears, while the ILD is the perceived volume difference in the signal.
For example, a sound that comes from the individual's right, will hit the right ear first with a slightly higher volume.

@@

The elevation estimation performance for both groups deteriorated when compared to their pan estimation results, which was somewhat expected given previous research results on human audition~\cite{barfield1997visual}. 
The mean absolute errors of the participants are \SI{0.37}{\radian} and \SI{0.51}{\radian} for groups \textit{G1} and \textit{G2} respectively.
As with the pan estimation errors, the participants from \textit{G1} seemed more adept at estimating the correct elevation.
%However, the difference is not as significant as for the pan, with \textit{G1} displaying a 36\% improvement over \textit{G2} in their elevation estimation vs. 42.5\% in the pan dimension. 
Comparing these results to methods that convey elevation through an HRTF, we see an improvement of approximately 46\% and 26\% for each group~\cite{schonstein2008comparison}. 
Indeed, the performance is comparable to that of open-back and expensive in-ear headphones.
There is a lesser improvement (11\%) with \textit{G1} when compared to the individualised and adjusted HRTFs in~\cite{stanley2006lateralization} and a 18\% reduction in performance for group \textit{G2}.
However, the participants from~\cite{stanley2006lateralization} all had healthy eyesight, making the latter comparison invalid. 
Interestingly, the elevation errors for group \textit{G2} are centred around the negative angle, indicating a possible underlying bias in the participants or the interface\todo{show}.
A similar trend was observed in~\cite{stanley2006lateralization} and warrants an investigation with a larger participant pool to determine the underlying bias, if any.

The error data was used to generate scatter plots that show the correlation between the position that the guidance system presented the participants and the position the participants thought the targets were.
These plots are given in \cref{fig:correlation-results} and show a reasonably positive correlation between the guidance targets and the selected targets, which indicates that the participants correctly interpreted the interface's output for the most part. 
The Pearson correlation scores for each dataset, listed in \cref{tab:results}, confirm this, as well as the negative angle bias in the elevation dimensions.

@@

Future work will involve a more in-depth investigation with a larger participant pool to determine the factors that affect performance and enable a more detailed statistical analysis.
For example, will adjusting the elevation function's gradient make it easier to guess the target's elevation and what is the performance difference between participants with limited and healthy eyesight?  
Furthermore, experiments with a large group of people with vision impairments will provide an opportunity to gauge their opinion on the interface and identify possible avenues of improvements to user friendliness.
Incorporating a progressive co-adaptation mechanism into the system, as suggested in~\cite{gallina2015progressive}, can also be considered to improve the overall user-friendliness and guidance performance.
